Model

### 2019-10-17 stats/model.Rmd
prepare model file for run

Infer({model,
      samples: 10,
      burn: 10,
      verbose: T,
      lag: 4,
      verboseLag: 5000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  packages = c("webppl_packages/webppl-sample-writer")
)

bind_rows(
sem_know_model <- read_csv("../saves/model/samples628.csv")%>%mutate(chain =1)
)

@@

sem_know_model <- readRDS("../saves/model_complete.rds")

>>>>

Infer({model,
      samples: 50000,
      burn: 250000,
      verbose: T,
      lag: 10,
      verboseLag: 5000,
      method: "incrementalMH",
      onlyMAP: true,
      callbacks: [callback]});
'
```

@@

```{r}
sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = data_comb_log),
  data_var = "dataFromR",
  model_var = "model",
  chains = 2,
  cores = 2,
  packages = c("webppl_packages/webppl-sample-writer")
)

read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
  saveRDS("../saves/model/chain_1.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
  saveRDS("../saves/model/chain_2.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
  saveRDS("../saves/model/chain_3.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
  saveRDS("../saves/model/chain_4.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
  saveRDS("../saves/model/chain_5.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
  saveRDS("../saves/model/chain_6.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =1)%>%
  saveRDS("../saves/model/chain_7.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
  saveRDS("../saves/model/chain_8.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
  saveRDS("../saves/model/chain_9.rds")

read_csv("../saves/model/samples434.csv")%>%mutate(chain =2)%>%
  saveRDS("../saves/model/chain_10.rds")

sem_know_model <- bind_rows(
  readRDS("../saves/model/chain_1.rds"),
  readRDS("../saves/model/chain_2.rds"),
  readRDS("../saves/model/chain_3.rds"),
  readRDS("../saves/model/chain_4.rds"),
  readRDS("../saves/model/chain_5.rds"),
  readRDS("../saves/model/chain_6.rds"),
  readRDS("../saves/model/chain_7.rds"),
  readRDS("../saves/model/chain_8.rds"),
  readRDS("../saves/model/chain_9.rds"),
  readRDS("../saves/model/chain_10.rds")
)

@@
